Selection of Polynomial Features by Genetic Algorithms

### 2013-07-22 texts/paper-draft.tex
adicionados ficheiros com imagens

\item find the fittest set of monomials, \emph{i.e.} the polynomial that minimizes the \ac{rmse} on the same dataset;
\end{enumerate}
%
More precisely, concerning the first problem, let $\mathcal{D}$ be a dataset with $N$ observations of variables $Y, X_1,\ldots,X_n$ and $\mathcal{M} = \left\lbrace m_1,\ldots, m_R\right\rbrace$ a set of $R$ monomial expressions over $X_1,\ldots,X_n$. Define the hypothesis\footnote{The expression $m|_{X=x}$ reads ``\emph{replace all instances of $X$ by $x$ in $m$}''.}
%
\begin{eqnarray*}
h_{\Theta,\mathcal{M}}\left(x_1,\ldots,x_n\right) &=& \sum_{j = 1}^R \theta_j m_j|_{X_i=x_i,\forall 1 \leq i \leq n}
\end{eqnarray*}
%
and let the cost
%
\begin{eqnarray}
J\left(\Theta;\mathcal{M},\mathcal{D}\right) &=& \sqrt{\frac{1}{N}\sum_{i=1}^N \left( y\sample{i} - h_{\Theta,\mathcal{M}}\left( x_1\sample{i},\ldots,x_n\sample{i} \right) \right)^2 }\label{eq:rmse}
\end{eqnarray}
%
be the usual \acf{rmse} function. Now the first problem can be stated as:
%
\begin{quote}
Given a dataset $\mathcal{D}$ and a set of monomials $\mathcal{M}$, find parameters $\Theta$ that minimize $J\left(\Theta;\mathcal{M},\mathcal{D}\right)$.
\end{quote}
%
It turns out that this problem can be solved as a usual linear regression problem by expanding $\mathcal{D}$ with columns that replicate the monomials in $\mathcal{M}$.

@@

This fitness function tends to prefer more complex polynomials, namely in the number of monomials which provides the regression algorithm for more fitting possibilities. One way to balance this is to provide a regularization term into the fitness function. Our proposal is to include a multiplicative factor into the fitness function proportional to the number of monomials. Thus, the fitness function from equation \ref{eq:rmse} becomes
\begin{eqnarray}
J_{fit}\left( \Theta; D \right) &=& \lambda^{m} \sqrt{ \frac{1}{n} \sum_{i=1}^n \left( y^{(i)} - h_{\Theta}\left(x_1^{(i)}, \ldots, x_m^{(i)}\right) \right)^2 }
\label{eq:rmse-reg}
\end{eqnarray}
%
where $m$ is the number of monomials the polynomial has. A $\lambda$ greater than one punishes polynomials with more monomials.

@@

\end{center}\end{figure}
%
%
\end{document}

\begin{figure}[tb]\begin{center}
\begin{tikzpicture}
\begin{axis}[width=\textwidth,height=6cm,
	boxplot/draw direction=y,
	xtick={1,2,3,4,5,6,7,8,9,10,11,12,13},
	xticklabels={0.70, 0.75, 0.80, 0.85, 0.90, 0.95, 1.00, 1.05, 1.10, 1.15, 1.20, 1.25, 1.30},
	xlabel={regularisation exponent ($\lambda$)},
	ymin=2.0,
	ymax=5.0,
	ylabel={Error distribution (\ac{rmse})},
	title={Error distribution by regularisation exponent (\textbf{Auto-MPG dataset})},
	mark options={scale=0.5},
	]	
	\pgfplotsset{boxplot/every box/.append style={fill=gray!50!white}}
	\addplot[boxplot] table [y index=0] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=1] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=2] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=3] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=4] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=5] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=6] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=7] {data/lambda.errors.Auto-Mpg.dat};		
	\addplot[boxplot] table [y index=8] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=9] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=10] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=11] {data/lambda.errors.Auto-Mpg.dat};
	\addplot[boxplot] table [y index=12] {data/lambda.errors.Auto-Mpg.dat};

\caption{Error distribution by regularisation exponent for the Auto-MPG dataset.}\label{Auto-MPG_dataset_lambdas}

>>>>

\item find the fittest set of monomials, \emph{i.e.} the polynomial that minimizes the \ac{rmse} on the same dataset;
\end{enumerate}
%
More precisely, concerning the first problem, let $\mathcal{D}$ be a dataset with $N$ observations of variables $Y, X_1,\ldots,X_n$ and $\mathcal{M} = \left\lbrace m_1,\ldots, m_R\right\rbrace$ a set of $R$ monomial expressions over $X_1,\ldots,X_n$. Define the hypothesis\footnote{The expression $m|_{X=x}$ reads ``\emph{replace all instances of $X$ by $x$ in $m$}''.}
%
\begin{eqnarray*}
h_{\Theta,\mathcal{M}}\left(x_1,\ldots,x_n\right) &=& \sum_{j = 1}^R \theta_j m_j|_{X_i=x_i,\forall 1 \leq i \leq n}
\end{eqnarray*}
%
and let the cost
%
\begin{eqnarray}
J_{fit}\left(\Theta;\mathcal{M},\mathcal{D}\right) &=& \sqrt{\frac{1}{N}\sum_{i=1}^N \left( y\sample{i} - h_{\Theta,\mathcal{M}}\left( x_1\sample{i},\ldots,x_n\sample{i} \right) \right)^2 }\label{eq:rmse}
\end{eqnarray}
%
be the usual \acf{rmse} function. Now the first problem can be stated as:
%
\begin{quote}
Given a dataset $\mathcal{D}$ and a set of monomials $\mathcal{M}$, find parameters $\Theta$ that minimize $J\left(\Theta;\mathcal{M},\mathcal{D}\right)$.
\end{quote}
%
It turns out that this problem can be solved as a usual linear regression problem by expanding $\mathcal{D}$ with columns that replicate the monomials in $\mathcal{M}$.

@@

This fitness function tends to prefer more complex polynomials, namely in the number of monomials which provides the regression algorithm for more fitting possibilities. One way to balance this is to provide a regularization term into the fitness function. Our proposal is to include a multiplicative factor into the fitness function proportional to the number of monomials. Thus, the fitness function from equation \ref{eq:rmse} defines
\begin{eqnarray}
J_{reg}\left(\Theta;\mathcal{M},\mathcal{D}\right) &=& \lambda^{m} J_{fit}\left(\Theta;\mathcal{M},\mathcal{D}\right)\label{eq:rmse-reg}
\end{eqnarray}
%
where $m$ is the number of monomials the polynomial has. A $\lambda$ greater than one punishes polynomials with more monomials.

@@
